DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-06-30 ase2017/paper.tex
reviewed section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{abstract}
We present an automated MATLAB Toolbox, named as DSSynth 
(Digital-System Synthesizer), to synthesize sound digital controllers 
for physical plants that are represented as linear time-invariant
systems with single input and output. In particular, DSSynth synthesizes digital 
controllers that are sound w.r.t. stability and safety specifications by taking into account finite word-length 
effects in their representation. DSSynth considers the complete range
of approximations, including time discretization, quantization effects, 
and finite-precision arithmetic (and its rounding errors). 
Currently, there are two DSSynth versions for synthesizing digital controllers for physical plants 
represented by transfer-function or state-space equations: a command-line and 
a MATLAB application. The resulting toolbox 
enables application of program synthesis to real-world control engineering systems.
\end{abstract}

@@

%Embedded digital control systems perform computations over digital signals 
%to influence the system behavior~\cite{Ogata2001}; it can be mathematically 
%expressed as difference equations, transfer functions or state-space equations. 
%Here, the focus is on transfer-function and state-space representations.

@@

The present tool paper addresses this limitation and describes a toolbox for the DSSynth tool~\cite{abate2017, abatecav2017} 
in a MATLAB environment, named \tool. The main advantage for the use of a MATLAB toolbox 
lies on designing physical plants in MATLAB and then promptly synthesizing a stable and safe digital controller,
considering the complete range of approximations. 
Additionally, when using the \tool, an engineer is able to model a physical plant with MATLAB, 
through transfer-function or state-space representations, considering low-level systems parameters 
(implementation features and numerical format), and then to synthesize a stable and safe digital controller.

@@

After that, the synthesis process starts in step $A$, when \tool obtains the digital system 
specification in MATLAB, and then translates it into an ANSI-C program. 
In step $B$, our CEGIS engine is invoked to synthesize the digital controller w.r.t. the digital system
specification. Finally, in step $C$, the synthesized digital controller considering FWL effects is produced. 
The output generated by \tool is the synthesized digital controller represented either in transfer function form 
or state-space format. The synthesis is considered to be \emph{successful} if a digital controller is correctly 
synthesized w.r.t. FWL effects; otherwise the synthesis is considered to be \emph{failed}, if any parameter is 
incorrectly defined in previous steps, or if there is no solution (digital controller) for the respective physical plant 
given the digital controller word length.

Our CEGIS engine is implemented as an integrated module within the bounded model checker CBMC~\cite{cbmc}.  CBMC
transforms an ANSI-C representation of our closed-loop control system model into its internal format called
\emph{GOTO}.  We instrument this internal \emph{GOTO} program for each synthesis or verification scenario accordingly,
and use CBMC as an oracle to answer our queries.  CBMC itself relies on an underlying SAT or SMT solver to solve the
resulting formulae.  We model FWL effects, time discretization and the presence of quantization noise explicitly using CBMC's  
nondeterminism API.  Our module was included in CBMC~5.7 and is available for
download\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}.  We further created a VirtualBox OVA image
with our tool pre-installed, including our MATLAB-generated benchmarks and benchmark shell script with instructions
to run all benchmarks and reproduce our
experiments\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}.  The current development branch
of our tool is available in a public GitHub
repository\footnote{\url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}.

The entire implementation consists of $400$ lines of MATLAB scripts for the UI
module, $585$ and $800$ lines of C code in the naive and abstract accelerator
model respectively.  $4000$ lines of C code for utility functions such as
interval and fixed-point arithmetic, as well as $1000$ lines of C++ code in the
control synthesis module in CEGIS CBMC.  We evaluate \tool using $20$ regression
test cases.

@@

The main objectives of our experimental evaluation is to (1) evaluate the \tool performance 
to produce stable controllers, and also (2) confirm the stability of the synthesized digital 
controllers outside of our model, using both the transfer-function and state-space representations.

>>>>

\begin{abstract}
We present an automated MATLAB Toolbox, named as DSSynth 
(Digital-System Synthesizer), to synthesize sound digital controllers 
for physical plants that are represented as linear time-invariant
systems with single input and output. In particular, DSSynth synthesizes digital 
controllers that are sound w.r.t. stability and safety specifications by taking into account finite word-length 
effects in their representation. DSSynth considers the complete range
of approximations, including time discretization, quantization effects, 
and finite-precision arithmetic (and its rounding errors). 
Currently, there are two DSSynth versions for synthesizing digital controllers for physical plants 
represented by transfer function or state-space equations: a command-line and 
a MATLAB application. The resulting toolbox 
enables application of program synthesis to real-world control engineering systems.
\end{abstract}

@@

%Embedded digital control systems perform computations over digital signals 
%to influence the system behavior~\cite{Ogata2001}; it can be mathematically 
%expressed as difference equations, transfer functions or state-space equations. 
%Here, the focus is on transfer function and state-space representations.

@@

The present tool paper addresses this limitation and describes a toolbox for the DSSynth tool~\cite{abate2017, abatecav2017} 
in a MATLAB environment, named \tool. The main advantage for the use of a MATLAB toolbox 
lies on designing physical plants in MATLAB and then promptly synthesizing a stable and safe digital controller,
considering the complete range of approximations. 
Additionally, when using the \tool, an engineer is able to model a physical plant with MATLAB, 
through transfer function or state-space representations, considering low-level systems parameters 
(implementation features and numerical format), and then to synthesize a stable and safe digital controller.

@@

After that, the synthesis process starts in step $A$, when \tool obtains the digital system 
specification in MATLAB, and then translates it into an ANSI-C program. 
In step $B$, our CEGIS engine is invoked to synthesize the digital controller w.r.t. the digital system
specification. Finally, in step $C$, the synthesized digital controller considering FWL effects is produced. 
The output generated by \tool is the synthesized digital controller represented either in transfer function 
or state-space equation. The synthesis is considered to be \emph{successful} if a digital controller is correctly 
synthesized w.r.t. FWL effects; otherwise, if any parameter is incorrectly defined in previous steps, 
or if there is no solution (digital controller) for the respective physical plant (given the digital controller
 implementation aspects), then the synthesis is considered to be \emph{failed}.

Our CEGIS engine is implemented as an integrated module within the C bounded model checker (CBMC)~\cite{cbmc}.  CBMC
transforms an ANSI-C representation of our closed-loop control system model into its internal format called
\emph{GOTO}.  We instrument this internal \emph{GOTO} program for each synthesis or verification scenario accordingly,
and use CBMC as an oracle to answer our queries.  CBMC itself relies on an underlying SAT or SMT solver to solve the
resulting formulae.  We model FWL effects, time discretization and the presence of quantization noise explicitly using CBMC's  
nondeterminism API (e.g., \texttt{nondet}, \texttt{CPROVER\_assume} intrinsic functions).  Our module was included in CBMC~5.7 and is available for
public download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}  We further created a VirtualBox OVA image
with our tool pre-installed, including our MATLAB-generated benchmarks and benchmark shell script with instructions
to run all benchmarks and reproduce our
experiments\.footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}  The current development branch
of our tool is available in a public GitHub
repository.\footnote{\url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}

The entire implementation consists of $400$ lines of MATLAB scripts for the UI
module, $585$ and $800$ lines of C code in the naive and abstract accelerator
model, respectively.  $4000$ lines of C code for utility functions such as
interval and fixed-point arithmetic, as well as $1000$ lines of C++ code in the
control synthesis module in CEGIS CBMC.  We evaluate \tool using about $20$ 
control system benchmarks.

@@

The main objectives of our experimental evaluation is to (1) evaluate the \tool performance 
to produce stable controllers, and also (2) confirm the stability of the synthesized digital 
controllers outside of our model, using both the transfer function and state-space representations.
